---
title: "shrub.open.shelter comparison"
author: "Nargol Ghazian"
date: "04/03/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library (tidyverse)
library(ggplot2)
#import datasets
panoche.climate.2019<-read.csv("C:/Users/Nargol Ghazian/Desktop/Animal-Behaviour-and-Climate-project/CH3/panoche_climate_hourly 2019.csv")

mean.daily.panoche <- read.csv("C:/Users/Nargol Ghazian/Desktop/Animal-Behaviour-and-Climate-project/CH3/weather station climate.csv")

str(panoche.climate.2019)
na.omit (panoche.climate.2019)#exclude missing values
head(is.na(panoche.climate.2019))#check for missing values
head(na.omit (mean.daily.panoche))
```


```{r}
##macro-climate plots
ggplot (panoche.climate.2019, aes((hour), air.temp)) + geom_smooth() + xlab("Hour (0-24)") + ylab ("Temperature (°C)")+  theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))#how air temperature changed during 24h period in 2019 during study period

ggplot (panoche.climate.2019, aes((day), air.temp)) + geom_smooth() + xlab("Day") + ylab ("Temperature (°C)")+  theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))#air temp over number of days

ggplot (panoche.climate.2019, aes((hour), soil.temp)) + geom_smooth() + xlab("Hour (0-24)") + ylab ("Temperature (°C)")+  theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))#how soil temperature changed during 24h period in 2019 during study period

ggplot (panoche.climate.2019, aes((day), soil.temp)) + geom_smooth() + xlab("Day") + ylab ("Temperature (°C)")+  theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))#how soil temperature changed during 24h period in 2019 during study period

ggplot (panoche.climate.2019, aes((hour), radiation)) + geom_smooth() + xlab("Hour (0-24)") + ylab ("Solar Radiation (W/m²)")+  theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))#how solar radiation changed during 24h period in 2019 during study period

ggplot (panoche.climate.2019, aes((day), radiation)) + geom_smooth() + xlab("Day") + ylab ("Solar Radiation (W/m²)")+  theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))

library (ggbeeswarm)
ggplot (panoche.climate.2019, aes((date), air.temp)) + geom_boxplot() + xlab("Date") + ylab ("Temperature (°C)")+ geom_quasirandom(alpha=0.05)+ theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))+ theme(axis.text.x = element_text(angle = 90))+ geom_smooth(se=FALSE, color="black", aes(group=1))#daily air temperature averages


```

```{r}
##micro-climate plots
##let's try some plots for shelter, shrub, and open

shelter.shrub.open <- read.csv("C:/Users/Nargol Ghazian/Desktop/Animal-Behaviour-and-Climate-project/CH3/shrub_contrast_final.csv")#import dataset

ggplot(shelter.shrub.open, aes((microsite), temp, fill=microsite)) + geom_boxplot() + xlab("Microsite") + ylab ("Temperature (°F)")+ theme_classic()+ theme(axis.text=element_text(size=12))+theme(axis.text.x = element_text(angle = 90))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ labs(fill = "Microsite")#not bad


ggplot(shelter.shrub.open, aes((microsite), intensity, fill=microsite)) + geom_boxplot() + xlab("Microsite") + ylab ("Solar Radiation (lum/ft²)")+ theme_classic()+ theme(axis.text=element_text(size=12))+theme(axis.text.x = element_text(angle = 90))+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ labs(fill = "Microsite")

ggplot(shelter.shrub.open, aes((day), temp, color=microsite)) + geom_smooth() + xlab("Day") + ylab ("Temperature (°F)")+ theme_classic()+ theme(axis.text=element_text(size=12))

ggplot(shelter.shrub.open, aes((day), intensity, color=microsite)) + geom_smooth() + xlab("Day") + ylab ("Solar Radiation (lum/ft²)")+ theme_classic()+ theme(axis.text=element_text(size=12))

#visualizing mean, median, and mode with histograms

ggplot(shelter.shrub.open, aes(temp, fill = microsite)) +
         geom_histogram(binwidth = 5) +
  scale_fill_brewer(palette = "Set1")+   labs(fill = "", x = "Temperature (°F)", y = "Frequency")+theme_classic()+ theme(axis.text=element_text(size=12))
#looks great you can report the actual numbers as well in the text

library(ggpubr)

ggplot(shelter.shrub.open, aes(temp, fill = microsite)) +
         geom_histogram(binwidth = 5) +
  scale_fill_brewer(palette = "Set1")+   labs(fill = "", x = "Temperature (°F)", y = "Frequency")+theme_classic()+ theme(axis.text=element_text(size=12))+ stat_central_tendency(aes(color = microsite), type = "mean", color="green", linetype = 2)+ stat_central_tendency(type = "median", color = "blue", linetype = 2)+ facet_grid(~microsite)+theme(legend.position = "none")

ggplot(shelter.shrub.open, aes(temp, fill = microsite)) +
         geom_density() +
  scale_fill_brewer(palette = "Set1")+   labs(fill = "", x = "Temperature (°F)", y = "Frequency")+theme_classic()+ theme(axis.text=element_text(size=12))

ggplot(shelter.shrub.open, aes(temp, fill = microsite)) +
         geom_density() +
  scale_fill_brewer(palette = "Set1")+   labs(fill = "", x = "Temperature (°F)", y = "Frequency")+theme_classic()+ theme(axis.text=element_text(size=12))+ stat_central_tendency(aes(color = microsite), type = "mean", color="green", linetype = 2)+ stat_central_tendency(type = "median", color = "blue", linetype = 2)+ facet_grid(~microsite)+theme(legend.position = "none")


```

```{r}
##model hypotheses
##pair-wise comparison
lm.temp <- glm(temp~as.factor(microsite), data = shelter.shrub.open, family="gaussian")
summary (lm.temp)
library (emmeans)
anova(lm.temp, test = "Chisq")
emmeans(lm.temp, pairwise~microsite)

lm.intensity <- glm(intensity~as.factor(microsite), data=shelter.shrub.open, family = "quasipoisson")
summary (lm.intensity)
anova(lm.intensity, test = "Chisq")
emmeans(lm.temp, pairwise~microsite)
emmeans (lm.intensity, pairwise~microsite)

```



```{r}

#let's create a heatmap
ggplot(shelter.shrub.open, aes(as.factor(day), as.factor(microsite), fill=temp))+ geom_tile()+ xlab("Day") + ylab ("Microsite")+theme(axis.text.x = element_text(angle = 90))+ scale_fill_distiller (palette='OrRd')+ theme_classic()+ labs(fill = "Temperature (°F)")

#geom_jitter plot for max and min of intensity for each microsite
ggplot(shelter.shrub.open, aes(x = as.factor(microsite), y = intensity)) +
  scale_y_log10() +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4) +
  stat_summary(fun.y = min, colour = "blue", geom = "point", size = 5) +
  stat_summary(fun.y = max, colour = "orange", geom = "point", size = 5)+ xlab("")+ ylab("Solar Radiation (lum/ft²)")+theme_classic()

#faceted by microsite
ggplot(shelter.shrub.open, aes(x = as.factor(day), y = intensity)) +
  scale_y_log10() +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4) +
  stat_summary(fun.y = min, colour = "blue", geom = "point", size = 5) +
  stat_summary(fun.y = max, colour = "orange", geom = "point", size = 5)+ xlab("Day")+ ylab("Solar Radiation (lum/ft²)")+theme_classic()+ facet_grid(~microsite)+ coord_flip()+ theme(axis.text.x = element_text(angle = 90))
```
```{r}
##test between macro-climate and micro-climate

macro.micro.contrast <- read.csv("C:/Users/Nargol Ghazian/Desktop/Animal-Behaviour-and-Climate-project/CH3/micro-macro-contrast.csv")

anova_temp_microsite <- aov(temp~microsite, data = macro.micro.contrast)
summary(anova_temp_microsite)
TukeyHSD(anova_temp_microsite)

ggplot(macro.micro.contrast, aes((microsite), temp, fill=microsite)) + geom_boxplot() + xlab("Site") + ylab ("Temperature (°F)")+ theme_classic()+ theme(axis.text=element_text(size=12))+theme(axis.text.x = element_text(angle = 90))+ theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+ labs(fill = "Site")
#weather station data are significantly differnt from shrub, open, and square.

```


##conclusions


#1. Macroclimate data from station looks great. Great addition to the paper. Boxplot-daily trend-line looks like a courser scale trendline from loggers, which is pretty interesting.
#2. Microclimate/logger data does not work well hourly...graph is too dense and clumped. Better as a daily plot. Fixed it and turned the lines into colours.
#3. Heat map looks great.
#4. Macro-climate data is significaly different from micro-climate. Loggers are a better predictor of fine scale abiotic changes.


```{r}
