---
title: "shrub.open.shelter comparison"
author: "Nargol Ghazian"
date: "04/03/2020"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library (tidyverse)
library(ggplot2)
#import datasets
panoche.climate.2019<-read.csv("C:/Users/Nargol Ghazian/Desktop/Animal-Behaviour-and-Climate-project/CH3/panoche_climate_hourly 2019.csv")

mean.daily.panoche <- read.csv("C:/Users/Nargol Ghazian/Desktop/Animal-Behaviour-and-Climate-project/CH3/weather station climate.csv")

str(panoche.climate.2019)
na.omit (panoche.climate.2019)#exclude missing values
head(is.na(panoche.climate.2019))#check for missing values
head(na.omit (mean.daily.panoche))
```


```{r}
ggplot (panoche.climate.2019, aes((hour), air.temp)) + geom_smooth() + xlab("Hour (0-24)") + ylab ("Temperature (°C)")+  theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))#how air temperature changed during 24h period in 2019 during study period

ggplot (panoche.climate.2019, aes((hour), soil.temp)) + geom_smooth() + xlab("Hour (0-24)") + ylab ("Temperature (°C)")+  theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))#how soil temperature changed during 24h period in 2019 during study period

ggplot (panoche.climate.2019, aes((hour), radiation)) + geom_smooth() + xlab("Hour (0-24)") + ylab ("Solar Radiation (W/m²)")+  theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))#how solar radiation changed during 24h period in 2019 during study period

library (ggbeeswarm)
ggplot (panoche.climate.2019, aes((date), air.temp)) + geom_boxplot() + xlab("Date") + ylab ("Temperature (°C)")+ geom_quasirandom(alpha=0.05)+ theme_classic()+ theme(axis.text=element_text(size=12))+ theme(axis.text=element_text(size=12))+ theme(axis.text.x = element_text(angle = 90))+ geom_smooth(se=FALSE, color="black", aes(group=1))#daily air temperature averages

library (cvequality)
temp.by.date <- 
with(panoche.climate.2019, 
     asymptotic_test(air.temp,date))#returns NA hmmm..need to think more about this

```

```{r}
##micro-climate plots

shelter.open <- read.csv("C:/Users/Nargol Ghazian/Desktop/Animal-Behaviour-and-Climate-project/CH3/Nargol_shelter_open.csv")

head(na.omit(shelter.open))
head(is.na(shelter.open))

ggplot(shelter.open, aes((day), temp, fill= timeblock)) + geom_smooth() + xlab("Day") + ylab ("Temperature (°F)")+ theme_classic()+ theme(axis.text=element_text(size=12))#works better by day rather than hour

ggplot(shelter.open, aes((day), temp, fill= microsite)) + geom_smooth() + xlab("Day") + ylab ("Temperature (°F)")+ theme_classic()+ theme(axis.text=element_text(size=12))#works better by day rather than hour

ggplot(shelter.open, aes((day), intensity, fill= timeblock)) + geom_smooth() + xlab("Day") + ylab ("Solar Radiation (lum/ft²)")+ theme_classic()+ theme(axis.text=element_text(size=12))#works better by day rather than hour or date 

ggplot(shelter.open, aes((day), intensity, fill= microsite)) + geom_smooth() + xlab("Day") + ylab ("Solar Radiation (lum/ft²)")+ theme_classic()+ theme(axis.text=element_text(size=12))#works better by day rather than hour or date 

##let's try some plots for shelter, shrub and open

shelter.shrub.open <- read.csv("C:/Users/Nargol Ghazian/Desktop/Animal-Behaviour-and-Climate-project/CH3/shelter_open_shrub.csv")#import dataset
head(na.omit (shelter.shrub.open))#get rid of NA's

ggplot(shelter.shrub.open, aes((day), temp, fill= microsite)) + geom_smooth() + xlab("Day") + ylab ("Temperature (°F)")+ theme_classic()+ theme(axis.text=element_text(size=12))#works better by day rather than hour

ggplot(shelter.shrub.open, aes((microsite), temp)) + geom_boxplot() + xlab("Microsite") + ylab ("Temperature (°F)")+ theme_classic()+ theme(axis.text=element_text(size=12))+theme(axis.text.x = element_text(angle = 90))#not bad

ggplot(shelter.shrub.open, aes((microsite), intensity)) + geom_boxplot() + xlab("Microsite") + ylab ("Solar Radiation (lum/ft²)")+ theme_classic()+ theme(axis.text=element_text(size=12))+theme(axis.text.x = element_text(angle = 90))

ggplot(shelter.shrub.open, aes((day), temp, fill=microsite)) + geom_smooth() + xlab("Day") + ylab ("Temperature (°F)")+ theme_classic()+ theme(axis.text=element_text(size=12))

```

```{r}
lm.temp <- glm(temp~as.factor(microsite), data = shelter.shrub.open, family="gaussian")
summary (lm.temp)
library (emmeans)
anova(lm.temp, test = "Chisq")
emmeans(lm.temp, pairwise~microsite)

lm.intensity <- glm(intensity~as.factor(microsite), data=shelter.shrub.open, family = "quasipoisson")
summary (lm.intensity)
anova(lm.intensity, test = "Chisq")
emmeans(lm.temp, pairwise~microsite)
##there are differences between the shelter and shrubs


```
##conclusions

#1. Still have to think about CV and mean. The most common way people plot is just a scatterplot. Not much else you can do except calculating them and putting them in table.
#2. Macroclimate data from station looks great. Great addition to the paper. Boxplot-daily trend-line looks like a courser scale trendline from loggers, which is pretty interesting.
#3. Microclimate/logger data does not work well hourly...graph is too dense and clumped. Better as a daily plot.
#4. There are differences between shrubs and shelters for both light and temperature. 

```{r}
